|

### 2021-06-21 coverletter.Rmd
Update coverletter.Rmd

We are excited to submit our manuscript entitled '*Emergent dual scaling of riverine biodiversity*' to *Proceedings of the National Academy Sciences*.

@@

In addition to the significance described above, the connection between network complexity and biodiversity has a broad implication for a truly interdisciplinary audience, including scientists working on fluvial geomorphology, network theory, and biodiversity. Our study is also timely given the unprecedented rate of global biodiversity loss in freshwater ecosystems. Therefore, *Proceedings of the National Academy Sciences* is an ideal outlet for this manuscript.

>>>>

We are excited to submit our manuscript entitled '*Emergent dual scaling of riverine biodiversity*' to *Proceedings of the National Academy of Sciences*.

@@

In addition to the significance described above, the connection between network complexity and biodiversity has a broad implication for a truly interdisciplinary audience, including scientists working on fluvial geomorphology, network theory, and biodiversity. Our study is also timely given the unprecedented rate of global biodiversity loss in freshwater ecosystems. Therefore, *Proceedings of the National Academy of Sciences* is an ideal outlet for this manuscript.
